Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/chokepoint.tex
Some additions, edits

\Ben[inline]{Include a little paragraph here about what this section describes}.

@@

\subsection{Border Nodes}

>>>>

In this section we motivate the choice to focus our analysis on border ASes and then
introduce and define out measure of chokepoint potential. We additionally introduce
the aggregate measure of chokepoint potential, national chokepoint potential (NCP)
for ranking and comparing nations according to the strength of their border AS chokepoints.

@@

\subsection{Border ASes}

### 2018-07-31 Paper/intro.tex
Some additions, edits

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet structure over time.  Current
methods have primarily focused on the node level (individual ASes)
rather than the country level\Steph[inline]{Josh Karlin and Jen Rexford papers are two exceptions and maybe there are more}, 
they have not described how AS topology
has changed over time with respect to national boundaries, and
existing BGP simulation methods make it difficult to address 
questions such as these efficienty and at scale.

\par
In this paper, we focus on the Autonomous Systems (AS) level of the Internet.
Autonomous Systems are groups of routers under common management, such as the network of
a university or an Internet Service Provider (ISP).
%The change in national AS topologies 
%is of interest to censorship research.
The total size of the AS graph (The global network 
of all ASes) has grown from about 10,000 ASes in the early 2000s to over 60,000 today. 
The structural properties of national subgraphs have evolved differently
from nation to nation whether from economic decision making, infrastructural necessities, 
or efforts to build a powerful censorship and surveillance network.\Ben[inline]{Need citations for economic, infrastructure, censorship}.
%The Autonomous Systems (AS) layer of the Internet has grown and changed dramatically over its history.
%The locations and relationships of these ASes determine how many chokepoints
%of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion, together with the changing role of national
governments, points to the importance of understanding properties like
path robustness, AS hierarchies, and the potential for organizations to
control information as it flows in and out of their networks.

>>>>

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet structure over time. Previous research has
investigated country level AS topology \cite{DBLP:journals/corr/abs-0903-3218},
focusing on how the global AS graph layout indicates that interdomain routing
for many Internet users depends on the infrastructure of other nations. We take
a different approach by developing a technique to monitor the amount of paths intercepted
by border ASes, allowing us to compare nations according to how BGP paths enter and exit
each nation.
% Current
% methods have primarily focused on the node level (individual ASes)
% rather than the country level, 
% they have not described how AS topology
% has changed over time with respect to national boundaries, and
% existing BGP simulation methods make it difficult to address 
% questions such as these efficienty and at scale.

\par
In this paper, we focus on the Autonomous Systems (AS) level of the Internet.
Autonomous Systems are groups of routers under common management, such as the network of
a university or an Internet Service Provider (ISP).
%The change in national AS topologies 
%is of interest to censorship research.
The total size of the AS graph (The global network 
of all ASes) has grown from about 10,000 ASes in the early 2000s to over 60,000 today. 
The structural properties of national subgraphs have evolved differently
from nation to nation whether from economic decision making, infrastructural necessities, 
or efforts to build a powerful censorship and surveillance network \cite{economicPeering, irancensor}.
%The Autonomous Systems (AS) layer of the Internet has grown and changed dramatically over its history.
%The locations and relationships of these ASes determine how many chokepoints
%of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion, together with the changing role of national
governments, points to the importance of understanding properties like
path robustness, AS hierarchies, and the potential for organizations to
control information as it flows in and out of their networks.

### 2018-07-31 Paper/results.tex
Some additions, edits

\section{Results}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesFree}
	\caption{The number of border ASes required for the US, France, Germany, and Great Britain to intercept 90\% of in-to-out paths over time.}\label{fig:nodesFree}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesCensor}
	\caption{The number of border ASes required for Russia, Egypt, Turkey, and China to intercept 90\% of in-to-out paths over time.}\label{fig:nodesCensor}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{multi}
	\caption{The capability for various nations to intercept in-to-out paths over multiple years \timerange. Each plot shows for a number of border ASes controlled (x-axis),
	what fraction of in-to-out paths are intercepted (y-axis). Years in blue are more recent, and years in red are further in the past.}\label{fig:multiTime}
\end{figure*}

We have chosen to detail the results of our experiment for 8 nations due to
their histories of censorship practice. First we have chosen 4 nations known to
enact extensive Internet censorship policies. These nations are China, Turkey,
Egypt, and Russia. China has historically been the number one nation in regards
to Internet censorship \cite{censorshipSurvey}. Turkey has recently
dramatically increased its online censorship efforts, by blocking social media
accesses during turmoil and pressuring ISPs to block access to material chosen
by the Turkish government \cite{turkeyCensor}. The Internet of Egypt suffered
severe shutdowns during the Arab Spring of the early 2010s \cite{arabspring}.
The Russian government has passed surveillance laws requiring ISPs to allow the
Russian government access to user statistics \cite{censorshipGeography}. Next
we have chosen the nations of Germany, the United States, France, and the
United Kingdom because, while they have all conducted limited forms of Internet
censorship \cite{censorshipSurvey}, Internet access for these nations is
considered highly open.

>>>>

\section{Experimental Results}

@@

	To evaluate national chokepoint potentials of each of these nations we
plot from our \toolname{} generated results the

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{nationsCompare}
	\caption{The national chokepoint potentials of various nations in 2018. k is the
	percentage of paths used to calculate the national chokepoint potential.}\label{fig:nationsCompare}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesFree}
	\caption{The number of border ASes required for the US, France, Germany, and Great Britain to intercept 90\% of in-to-out paths over time.}\label{fig:nodesFree}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{NodesCensor}
	\caption{The number of border ASes required for Russia, Egypt, Turkey, and China to intercept 90\% of in-to-out paths over time.}\label{fig:nodesCensor}
\end{figure}
\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{multi}
	\caption{The capability for various nations to intercept in-to-out paths over multiple years \timerange. Each plot shows for a number of border ASes controlled (x-axis),
	what fraction of in-to-out paths are intercepted (y-axis). Years in blue are more recent, and years in red are further in the past.}\label{fig:multiTime}
\end{figure*}

We have chosen to detail the results of our national chokepoint potential
experiment for 8 nations due to
their histories of censorship practice. First we have chosen 4 nations known to
enact extensive Internet censorship policies. These nations are China, Turkey,
Egypt, and Russia. China has historically been the number one nation in regards
to Internet censorship \cite{censorshipSurvey}. Turkey has recently
dramatically increased its online censorship efforts, by blocking social media
accesses during turmoil and pressuring ISPs to block access to material chosen
by the Turkish government \cite{turkeyCensor}. The Internet of Egypt suffered
severe shutdowns during the Arab Spring of the early 2010s \cite{arabspring}.
The Russian government has passed surveillance laws requiring ISPs to allow the
Russian government access to user statistics \cite{censorshipGeography}. Next
we have chosen the nations of Germany, the United States, France, and the
United Kingdom because, while they have all conducted limited forms of Internet
censorship \cite{censorshipSurvey}, Internet access for these nations is
considered highly open.
